QPLIB: A Library of Quadratic Programming Instances

### 2016-12-27 QPLIB-1.0.tex
Update QPLIB-1.0.tex

\multirow{1}{.55\textwidth}{{\bf Finance:} Portfolio optimization} & checkmark & \multirow{1}{.25\textwidth}{\cite{deng-etal:2013,kallrath:2003,lin-etal:2005,maranas-etal:1997,parpas-rustem:2006,rios-sahinidis:2010,FrFG16,FrGe06a,FrGe07a,FrGe09a}} \\ 

>>>>

\multirow{1}{.55\textwidth}{{\bf Finance:} Portfolio optimization} & \checkmark & \multirow{1}{.25\textwidth}{\cite{deng-etal:2013,kallrath:2003,lin-etal:2005,maranas-etal:1997,parpas-rustem:2006,rios-sahinidis:2010,FrFG16,FrGe06a,FrGe07a,FrGe09a}} \\ 
